---
title: "Integer Programming"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
date: "2022-11-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#importing lpsolve library for current environment
```{r}
library("lpSolveAPI")
```

#importing lp for current integer problem
```{r}
setwd("/Users/thupiliabhinav/Desktop/QMM/Integer programming")
int_file <- read.lp("integer_file.lp")
print(int_file)
```
#day workers required under current constraints
```{r}
day_workers <- matrix(c("Sunday","Monday","Tuesday","Wednesday","Thursday","Friday","Saturday",
18,27,22,26,25,21,19),ncol=2,byrow = F)

colnames(day_workers) <- c("day_of_the_week", "workers_required")

as.table(day_workers)
```
#Package handlers at AP are guaranteed a five-day work week with two consecutive days off. The base wage for the handlers is $750 per week. Workers working on Saturday or Sunday receive an additional $25 per day. The possible shifts and salaries for package handlers are:
```{r}
day_offs_and_wages <- matrix(c(1,2,3,4,5,6,7,
                               "Sunday and Monday","Monday and Tuesday","Tuesday and Wednesday","Wednesday and Thursday","Thursday and Friday","Friday and Saturday","Saturday and Sunday",
                               "$775","$800","$800","$800","$800","$775","$750"),ncol=3,byrow=F)

colnames(day_offs_and_wages) <- c("Shift", "Days_Off", "Wage")

as.table(day_offs_and_wages)
```
#creating lp model.
```{r}
solve(int_file)
```
#The formulation of lp was successful as the value returned is 0.


#Objective Function.
```{r}
get.objective(int_file)
```
#Total wages expenses for our objective function is $25,675 for AP shipping service.


```{r}
get.variables(int_file)
```
#Interpretation:
#From above we can observe the following:
#Worker Assigned in shift 1 = 2.
#Worker Assigned in shift 2 = 4.
#Worker Assigned in shift 3 = 5.
#Worker Assigned in shift 4 = 0.
#Worker Assigned in shift 5 = 8.
#Worker Assigned in shift 6 = 1.
#Worker Assigned in shift 7 = 13.

#From above variables we can derive the objective function and constraints for the below model.
#Sunday: x2 + x3 + x4 + x5 + x6 = 18;
#Monday: x3 + x4 + x5 + x6 + x7 = 27;
#Tuesday: x4 + x5 + x6 + x7 + x1 = 22;
#Wednesday: x5 + x6 + x7 + x1 + x2 = 26;
#Thursday: x6 + x7 + x1 + x2 + x3 = 25;
#Friday: x7 + x1 + x2 + x3 + x4 = 21;
#Saturday: x1 + x2 + x3 + x4 + x5 = 19;
