---
title: "Transportation Assignment"
date: "2022-10-11"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##set transportation matrix

```{r}
library(lpSolve)
library(lpSolveAPI)
cost1<- matrix(c(22,14,30,600,100,
                    16,20,24,625,120,
                    80,60,70,"-","-"),ncol=5,byrow= TRUE)
colnames(cost1)<- c("Ware1","Ware2","Ware3","ProdnCost","ProdnCapacity")
rownames(cost1)<-c("P.A","P.B"," Demand")
cost1
```


#Objective function = Minimize the Transportation Cost
Min TC = 622x11 + 614x12 + 630x13 + 0x14 + 641x21 + 645x22 + 649x23 + 0x24


#Subject to constraints : Supply
X11 + X12 + X13 + X14 <= 100 X21 + X22 + X23 + X24 <= 120

#Subject to constraints : Demand
X11 + X21 >= 80 X12 + X22 >= 60 X13 + X23 >= 70 X14 + X24 >= 10

#Non-Negativity Constraints
Xij >= 0
Where i = 1,2 and j= 1,2,3,4 #The capacity = 220 and Demand = 210. We will add a “Dummy” row for
Warehouse_4.

```{r}
transportation.cost.1<- matrix(c(622,614,630,0,
                 641,645,649,0),ncol =4, byrow=TRUE)
transportation.cost.1
```

##Constraints of r.h.s(supply side)
```{r}
rsigns<- rep("<=",2)
rrhs<- c(100,120)
```

#Supply func. cannot be greater than the specified units
##Demand Side
```{r}
csigns<- rep(">=",4)
crhs<- c(80,60,70,10)
```

##demand function can be greater

```{r}
library(lpSolve)
lptransmodel<-lp.transport(transportation.cost.1,"min",rsigns,rrhs,csigns,crhs)
lptransmodel$solution
```
#80 AEDs in Plant2 - Warehouse1 
#60 in Plant1 - Warehouse2 
#40 AEDs in Plant1 - Warehouse3
#30 AEDs in Plant2 - Warehouse3 

#Warehouse capacity is 220 which is distributed bewtween 3 warehouses Plant2 is producing 80 products in Warehouse1, plant1 is producing 60products in Warehosue2. Plant1 is producing 40 products in Warehouse3.

##Value of nvariables
```{r}
lptransmodel$objval
```

#Cost of production and shipping for the defibrilators is $132,790

```{r}
lptransmodel$duals
```

#2. Dual of transportation problem - The primal was to minimize the transportation cost the dual of it would be to maximize the valueadded(VA). a and b will be the variables for the dual.

```{r}
cost2<-matrix(c(622,614,630,100,"x1",
                 641,645,649,120,"x2",
                 80,60,70,220,"-","y1","y2","y3","-","-"),ncol = 5,nrow=4,byrow=TRUE)

colcost.2 <- c("W1", "W2","W3","Production Capacity","Supply(Dual)")
rowcost.2 <- c("A","B","Demand","Demand(Dual)")
```

#Objective function

```{r}
f.obj <- c(100,120,80,60,70)
```

#Transposed from the constraints matrix in the primal
```{r}
f.con <- matrix(c(1,0,1,0,0,
1,0,0,1,0,
1,0,0,0,1,
0,1,1,0,0,
0,1,0,1,0,
0,1,0,0,1), nrow = 6, byrow = TRUE)
f.dir <- c("<=",
"<=",
"<=",
"<=",
"<=",
"<=")
f.rhs <- c(622,614,630,641,645,649)
lp("max",f.obj,f.con,f.dir,f.rhs)
```
## Success: the objective function is 139120

```{r}
lp("max",f.obj,f.con,f.dir,f.rhs)$solution
```

#Z=139,120 and variables are:
#x1 = 614 x2 = 633 y1 = 8 y3 = 16

#3. Economic Interpretation of the dual 

#Economic Interpretation of the dual is, the minimal Z(Primal) = 132790 and the maximum Z(Dual) = 139120. We should not be shipping from Plant(A/B) to all the three Warehouses. We should be shipping from:

#60X12 which is 60 Units from Plant A to Warehouse 2. 
#40X13 which is 40 Units from Plant A to Warehouse 3. 
#80X13 which is 60 Units from Plant B to Warehouse 1. 
#30X13 which is 60 Units from Plant B to Warehouse 3. 
#We will Max the profit from each distribution to the respective capacity.


```{r}
rrhs1 <- c(101,120)
rsigns1 <- rep("<=",2)
crhs1 <- c(80,60,70,10)
csigns1 <- rep(">=",4)
rrhs2 <- c(100,121)
rsigns2 <- rep("<=",2)
crhs2 <- c(80,60,70,10)
csigns2 <- rep(">=",4)
lp.transport(transportation.cost.1,"min",rsigns,rrhs,csigns,crhs)
```

```{r}
lp.transport(transportation.cost.1,"min",rsigns1,rrhs1,csigns1,crhs1)
```

```{r}
lp.transport(transportation.cost.1,"min",rsigns2,rrhs2,csigns2,crhs2)
```

```{r}
lp("max", f.obj,f.con, f.dir,f.rhs)$solution

```

